%------------------
%   Information
%------------------

\newcommand{\userfull}{
    Jesús González
}
\newcommand{\userdiploma}{
    B.S. in Computer Science and Technology
}
\newcommand{\usernumbwork}{
    \docplus 52 222 265 0774
}
\newcommand{\usernumbmain}{
    \docplus 52 271 108 5129
}
\newcommand{\usermail}{
    jesugq@gmail.com
}
\newcommand{\username}{
    jesugq
}
\newcommand{\userchat}{
    Messengers
}
\newcommand{\userpost}{
    Puebla, Puebla
}

%------------------
%   Sections
%------------------

\newcommand{\projects}{
    Projects
}
\newcommand{\experience}{
    Experience
}
\newcommand{\education}{
    Education
}
\newcommand{\skills}{
    Competences
}
\newcommand{\current}{
    \makebox[\widthof{ 00/0000}]{Current}
}
\newcommand{\greetings}{
    Greetings
}

%------------------
%   Profile
%------------------

\newcommand{\titleprofile}{
    Firm believer and example that willing people can change. Young engineer studying Full-Stack technologies with a high affinity for self-learning.
}

%------------------
%   Education
%------------------

\newcommand{\timeodin}{
    03 / 2021 — \current
}
\newcommand{\titleodin}{
    The Odin Project
}
\newcommand{\subtitleodin}{
    Puebla, Puebla
}
\newcommand{\descriptionodin}{
    \docitemize{
        \item Currently practicing with an updated Full Stack curriculum.
    }
}

\newcommand{\timeengineer}{
    08 / 2015 — 06 / 2020
}
\newcommand{\titleengineer}{
    Tecnológico de Monterrey
}
\newcommand{\subtitleengineer}{
    Puebla, Puebla
}
\newcommand{\descriptionengineer}{
    \docitemize{
        \item Graduated in B.S. Computer Science and Technology.
    }
}

%------------------
%   Projects
%------------------

\newcommand{\timehomepage}{
    04 / 2021
}
\newcommand{\titlehomepage}{
    Google Homepage
    \doclink{https://jesugq.github.io/google-homepage/}{faGlobe}
}
\newcommand{\subtitlehomepage}{
    HTML, CSS, Flexbox
}
\newcommand{\descriptionhomepage}{
    \docitemize{
        \item Recreation of the google homepage using a single HTML and CSS file.
        \item Implementation of the Flexbox layout to support ample screen sizes and layouts.
        \item Usage of normalize css to further improve design similarity between browsers.
    }
}

\newcommand{\timeportfolio}{
    03 / 2021
}
\newcommand{\titleportfolio}{
    Responsive Portfolio
    \doclink{https://github.com/jesugq/responsive-design}{faGithub}
}
\newcommand{\subtitleportfolio}{
    HTML, CSS, Flexbox, Grid
}
\newcommand{\descriptionportfolio}{
    \docitemize{
        \item Creation of 5 responsive web pages using only HTML and CSS.
        \item Implementation of Flexbox and Grid layouts to support a variable quantity of elements on the page.
        \item Usage of established patterns to grant accessibility to the page for users with reading assistants.
    }
}

\newcommand{\timesudoku}{
    01 / 2021
}
\newcommand{\titlesudoku}{
    Sudoku Solver
    \doclink{https://github.com/jesugq/sudoku}{faGithub}
}
\newcommand{\subtitlesudoku}{
    Python, Pytest
}
\newcommand{\descriptionsudoku}{
    \docitemize{
        \item Object-oriented, test-driven implementation of the Backtracking Sudoku Solving Algorithm.
        \item Design of 4 single-purpose modules, each with a test module dictating the use cases to comply with.
        \item Optimized the solving algorithm to execute a maximum of 1.4 seconds, down from 3.7 seconds.
    }
}

\newcommand{\timefinance}{
    04 / 2020
}
\newcommand{\titlefinance}{
    Finance \& Stocks
    \doclink{https://github.com/jesugq/finance}{faGithub}
}
\newcommand{\subtitlefinance}{
    Python, Flask, SQLite
}
\newcommand{\descriptionfinance}{
    \docitemize{
        \item Development of a web application to simulate the purchasing and selling of market shares with real prices.
        \item Operations done using prices obtained from the IEX Cloud API and stored on a SQLite database.
        \item Working implementation of 4 tables for users, shares per users, purchases and sales in SQL.
    }
}

\newcommand{\timecompiler}{
    11 / 2019
}
\newcommand{\titlecompiler}{
    Basic Compiler
    \doclink{https://github.com/jesugq/compiler-simplified-syntax-tree}{faGithub}
}
\newcommand{\subtitlecompiler}{
    C, Flex, Bison
}
\newcommand{\descriptioncompiler}{
    \docitemize{
        \item Implementation of a compiler that recognizes left-derived grammars with 3 modules and 3 headers.
        \item Usage of a simplified syntax tree structure to store instructions to follow in order.
        \item Variables and functions stored in a symbol table using a hash table.
    }
}

\newcommand{\timekubeet}{
    05 / 2018
}
\newcommand{\titlekubeet}{
    Kubeet Web
    \doclink{https://github.com/jesugq/kubeet-landing}{faGithub}
}
\newcommand{\subtitlekubeet}{
    Typescript, Angular, Firebase
}
\newcommand{\descriptionkubeet}{
    \docitemize{
        \item Creation of 13 Angular components to present a single page application similar to Udemy.
        \item Implementation of a catalog view of self-study material, consisting of video and text lessons.
        \item Storage and retrieval of data using an external source, Firebase.
    }
}

\newcommand{\timecrafter}{
    05 / 2018
}
\newcommand{\titlecrafter}{
    Crafter Mobile
    \doclink{https://github.com/jesugq/WCrafter-iOS}{faGithub}
}
\newcommand{\subtitlecrafter}{
    Swift, Xcode
}
\newcommand{\descriptioncrafter}{
    \docitemize{
        \item Creation of 13 Swift components managing a bus monitoring prototype app for the iOS platform.
        \item Implementation of 2 responsive tables and 5 interfaces accessible from the application's home menu.
    }
}

%------------------
%   Experience
%------------------

\newcommand{\timetutor}{
    08 / 2018 — 11 / 2018
}
\newcommand{\titletutor}{
    Online Tutor Intern
}
\newcommand{\subtitletutor}{
    \docbold{Prep@Net} in Puebla, Puebla
}
\newcommand{\descriptiontutor}{
    \docitemize{
        \item Follow-up of 12 students during their studies, supporting them in learning Word and Excel.
        \item Each monday they were given a weekly agenda to learn their responsibilities for the following week.
        \item Assesment of their homework every friday, in addition to giving advice at the times scheduled by the student.
    }
}

\newcommand{\timeit}{
    01 / 2016 — 04 / 2016
}
\newcommand{\titleit}{
    IT Intern
}
\newcommand{\subtitleit}{
    \docbold{ITESM CCV} in Fortin, Veracruz
}
\newcommand{\descriptionit}{
    \docitemize{
        \item Maintenance of more than 6 Windows work computers per week, cleaning temporary files.
        \item Installation of office applications such as Microsoft Office, Adobe Library, and other time-management apps.
    }
}

%------------------
%   Skills
%------------------

\newcommand{\titlesoftskills}{
    Soft Skills
}
\newcommand{\subtitlesoftskills}{
    Proactive, Organized, Responsible, Autodidactic, Early bird (4am), Player—Learner.
}
%   Personal:   Proactive, Organized, Responsible, Adaptable, Transparent
%   External:   NativeSpanish
%   Learning:   Autodidactic, Self-improving
%   Mentality:  Player-Learner Mentality
%   Routine:    EarlyBird4AM

\newcommand{\titlelanguages}{
    Languages
}
\newcommand{\subtitlelanguages}{
    Java, Python, MySQL, MongoDB, SQLite, Javascript, HTML, CSS.
}
%   Functional:             C
%   Object Oriented:        Java Python
%   Databases:              SQL SQLite MySQL MongoDB
%   Web Development:        Javascript HTML CSS HTML5 CSS5

\newcommand{\titletechnologies}{
    Technologies
}
\newcommand{\subtitletechnologies}{
    Windows 10, Fedora Linux, Git, Bash, LaTeX \href{https://github.com/jesugq/resume}{\docicon{faGithub}}, Microsoft Office, Google Suite.
}
%   Operating System:       Windows, Linux (Fedora)
%   Terminal:               Git Bash
%   Web Development:        Angular Angular7 React ReactNative
%   Office Suites:          Latex MicrosoftOffice GoogleSuite

\newcommand{\titlestudies}{
    Relevant

    \hspace{0pt}
    Studies
}
\newcommand{\subtitlestudies}{
    Software engineering, Software design and architecture, Business solution development,

    Analysis and design of algorithms, Data structures, Computational mathematics.
}
%   Engineering:            ComputerOrganization OperatingSystems
%                           ProgrammingLanguages SoftwareEngineering
%   Project Management:     AnalysisAndModellingOfSoftwareSystems
%                           ProjectEvaluationAndManagement
%                           ManagementOfSoftwareEngineeringProjects
%                           SoftwareDesignAndArchitecture
%                           BusinessSolutionDevelopment
%   Quality Assurance:      SoftwareQualityAndTesting SelfDocumentedCode
%                           TestDrivenDevelopment
%   Math and Probability:   ComputationalMathematics ProbabilityAndStatistics
%                           NumericalMethodsInEngineering
%                           QuantitativeMethodsAndSimulation
%   Algorithms:             DataStructures AnalysisAndDesignOfAlgorithms
%   Functional:             AdvancedProgramming CompilerDesign
%   Object Oriented:        Object-OrientedProgramming
%   Mobile Development:     MobileApplicationDevelopment
%   Web Development:        WebApplicationsDevelopment  ComputerGraphics
%                           ResponsiveWebDesign
%   Databases:              AdvancedDatabaseSystems NetworkInterconnection

%------------------
%   Cover Letter
%------------------

\newcommand{\coverletter}{
    Dear human resources manager,\\\\\\

    Below this letter you will find my resume. I found your position today in — and wish to know more about you and your team.\\

    I'm a young engineer and practitioner of full-stack development, looking to develop real world solutions and know the processes carried out by today's organizations. I have a fondness for reading, music, cold climates, and the study of engineering—technology subjects, for which I want to learn how you perform your operations and show you that I can be a great addition to your development team.\\

    Your position requires — , requirements in which I have experience because of — .\\

    I appreciate your time reading this letter, and the opportunity you present for us young engineers. Feel free to contact me through my phone {\normalsize\textbf{+52 222 265 0774}}, my e-mail {\normalsize\textbf{jesugq@gmail.com}} or any of the three interactable icons at the top of this document. I wish you this — .\\\\\\

    Sincerely,\\
    Jesús Antonio González Quevedo
}